Quality of weight Lifting Exercises
========================================================

The goal is to create model predicting if excercises were done in proper way (Class A) or with one of common mistakes (Class B to E)

Loading datasets
-----------------

First I load data sets, because of epmty values I replace them with NA


```{r}
trainset  <- read.csv("pml-training.csv", header=TRUE, na.strings = c("", " ","NA"))
testset  <- read.csv("pml-testing.csv", header=TRUE, na.strings = c("", " ","NA"))
```

Preprocessing
-------------
To create training and testing datasets I use caret and randomFores package

First I get rid of near zero variance predictors
```{r}
library(caret)
library(randomForest)
nsv <- nearZeroVar(trainset,saveMetrics=FALSE)
trainset<-trainset[,- nsv]
```

Time series variables are not usefull for model creation so I throw away cols: 1, 2, 3, 4, 5, 6

```{r}
trainset<-trainset[,-c(1,2,3,4,5,6)]
```

There are some variables in dataset which are treated as categorical and have '#DIV/0' value, like kurtosis_roll_belt for example I will omit them in model

```{r}
num<-lapply(trainset[1,],is.numeric)
length(num)
num<-num[-111]
trainset<-trainset[,num==TRUE]
```


Model creation
--------------

I will use cross-validation, I will validate model using subset of data from training set

```{r}
set.seed(333)
inTrain <- createDataPartition(y=trainset$classe,
                               p=0.70, list=FALSE)
training <- trainset[inTrain,]
testing <- trainset[-inTrain,]
```


There is a lot of NA values in dataset in few collumns so variability is not so good (rather smaller than expected).
I will use random forests classification so.
Because of predictors with low variability I suppouse that model will have accuracy about 0.65 - 0.70. 

For model and prediction I use random forest algorithm

```{r}
modFit<-randomForest(classe ~ ., data = training, na.action=na.omit) 
modFit
summary(modFit)

pred<-predict(modFit, testing)
confusionMatrix(pred, testing$classe)
```

As we can see model has 0.769  Accuracy for testing data


For training data Accuracy is of course equal 1

```{r}
pred<-predict(modFit, training)
confusionMatrix(pred, training$classe)
```



